---
title: "Applications of Longitudinal Machine Learning Methods in Multi-Study Alzheimer’s Disease Datasets"
subtitle: "PhD Dissertation Defense for<br>Doctorate Degree in Biostatistics"
author: "Charles Murchison"
institute: "Department of Biostatistics<br>Alzheimer's Disease Research Center"
date: "11/10/2021"
output:
  xaringan::moon_reader:
    css: [default, robot, robot-fonts, extra.css]
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    lib_dir: libs
    nature:
      titleSlideClass: ["center", "middle"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
suppressPackageStartupMessages({
  library(shiny)
  library(knitr)
  library(kableExtra)
  library(ggplot2)
})

options(knitr.kable.NA = '')
opts_chunk$set(tidy = FALSE)

boot_dat <- readRDS("boot_data.rds")
comp_table <- readRDS("boot_compare.rds")

theme_explorer <- 
  ggplot2::theme_bw() + 
  ggplot2::theme(legend.title=ggplot2::element_blank(), legend.background=ggplot2::element_blank(), legend.position="bottom") + 
  ggplot2::theme(plot.title=ggplot2::element_text(hjust=0.5, size=24)) +
  ggplot2::theme(axis.title=ggplot2::element_text(size=18), axis.text=ggplot2::element_text(size=14)) + 
  ggplot2::theme(legend.text=ggplot2::element_text(size=12))

theme_manus <- 
  ggplot2::theme_classic() + 
  ggplot2::theme(legend.title=ggplot2::element_blank(), legend.background=ggplot2::element_blank(), legend.position="bottom") + 
  ggplot2::theme(plot.title=ggplot2::element_text(hjust=0.5, size=24)) +
  ggplot2::theme(axis.title=ggplot2::element_text(size=18), axis.text=ggplot2::element_text(size=11)) + 
  ggplot2::theme(legend.text=ggplot2::element_text(size=12))





#Some table processing functions

table_proc_cont <- function(.tab){
  
  .tab$Value <- round(.tab$Value, 3)
  
  .out <- data.frame(Time=unique(.tab$time))
  .out$RMSE <- .tab$Value[.tab$Metric=="RMSE"]
  .out$MAE <- .tab$Value[.tab$Metric=="Median AE"]
  .out$Bias <- .tab$Value[.tab$Metric=="Bias"] * -1
  
  
  rownames(.out) <- NULL
  return(.out)
}



table_proc_cat <- function(.tab){
  
  .tab$Value <- round(.tab$Value, 4)
  
  .out <- data.frame(Time=unique(.tab$time))
  .out$Accuracy <- .tab$Value[.tab$Metric=="Accuracy"]
  .out$Precision <- .tab$Value[.tab$Metric=="Precision"]
  .out$Recall <- .tab$Value[.tab$Metric=="Recall"]
  .out$AUC <- .tab$Value[.tab$Metric=="AUC"]
  
  if("NRI" %in% .tab$Metric) .out$NRI <- .tab$Value[.tab$Metric=="NRI"]
  
  rownames(.out) <- NULL
  return(.out)
  
  
}


tab_proc_hyper <- function(.tab){
  .tab$Value <- round(.tab$Value, 4)
  .tab$Value[.tab$Metric=="Bias"] <- .tab$Value[.tab$Metric=="Bias"] *-1
  colnames(.tab) <- c("Metric", "Value", "Hyperparameters")
  
  if(length(grep("layer_count", .tab$Hyperparameters))>0){
    .tab$Hyperparameters <- gsub("(dense|cnn|lstm)_[1-3]_(activ|kern_constraint|bias_constraint|pool_size|kernel_size)(.*?)(;|NULL|relu)", "", .tab$Hyperparameters)
    .tab$Hyperparameters <- gsub(";\\s*;", ";", .tab$Hyperparameters)
  }
  
  rownames(.tab) <- NULL
  return(.tab)
  
}

metric_list <- list(old_col = c("RMSE", "Median AE", "Bias", "Accuracy", "Precision", "Recall", "AUC"),
                     new_col = c("RMSE", "MAE", "AV Bias", "Accur", "Prec", "Recall", "AUC"))

tab_proc_boot <- function(.boot, .pred, .ref, drop_time = TRUE){
  .boot$Diff <- round(.boot$Diff, 3)
  .boot$Prop_diff <- gsub(" ", "", .boot$Prop_diff)
  .boot$Boot_p <- gsub(" ", "", .boot$Boot_p)
  
  .pred$Value <- round(.pred$Value, 3)
  .ref$Value <- round(.ref$Value, 3)
  
  if("Bias" %in% .pred$Metric){
    .pred$Value[.pred$Metric]
  }
  
   if("NRI" %in% .pred$Metric){
     nri_curr <- paste0("NRI: ", .pred$Value[.pred$Metric == "NRI"])
   }
  
  .boot <- .boot[.boot$Metric %in% metric_list$old_col,]
  .pred <- .pred[.pred$Metric %in% metric_list$old_col,]
  .ref <- .ref[.ref$Metric %in% metric_list$old_col,]
  
  .boot$Metric <- metric_list$new_col[which(metric_list$old_col %in% .boot$Metric)]
  .pred$Metric <- metric_list$new_col[which(metric_list$old_col %in% .pred$Metric)]
  .ref$Metric <- metric_list$new_col[which(metric_list$old_col %in% .ref$Metric)]
  
  
  if(drop_time == TRUE){
    .boot <- .boot[,-which(colnames(.boot)=="time")]
    .pred <- .pred[,-which(colnames(.pred)=="time")]
    .ref <- .ref[,-which(colnames(.ref)=="time")]
  }
  
    
  .out <- data.frame(Metric = .pred$Metric, V2 = .pred$Value, V3 = .ref$Value, .boot[,colnames(.boot) %in% c("Diff", "Prop_diff", "Boot_p")])
  colnames(.out) <- c("Metric", "ML Model", "Ref Model", "Delta", "Perc Diff", "Boot P")
  rownames(.out) <- NULL
  
  if(exists("nri_curr")){
    return(list(tab = .out, NRI = nri_curr))
  } else  return(list(tab = .out))
}






#Functions to rebuild the plots from the ggplot data



plot_diff_adas_rebuild <- function(.dat){
  
  group_var <- "time"
  outcome <- "ADASTOTAL11"
  plot_curr <- 
  ggplot(data=.dat, aes_string(x = "time", y = "diff")) + 
        geom_point(aes(color = misclass), position = position_jitter(width=0.15), size = 2) + 
        geom_hline(yintercept = 0, color = "red") + 
        geom_errorbar(stat = "summary", fun.data = "mean_sdl", fun.args = list(mult=1), width = 0.2, size = 1.25, alpha = 0.45) + 
        stat_summary(fun = mean, geom = "point", shape = 45, size = 18) +
        
        scale_x_continuous(name = "Years", breaks = c(0:100), labels=c(0:100)) + 
        scale_y_continuous(name = paste0("ADAS-Cog:", " Predict - Actual")) +
        scale_color_brewer(type = "qual", palette = "Set1") +
        expand_limits(x = c(min(.dat[[group_var]], max(.dat[[group_var]])))) + 
        
        theme_explorer
  
  return(plot_curr)
}

plot_pred_adas_rebuild <- function(.dat){
  
  outcome <- "ADASTOTAL11"
  group_var <- "time"
  
   plot_curr <- 
        ggplot(data = .dat, aes_string(x = group_var, y = outcome)) + 
        geom_point(aes(color = Type), position = position_jitterdodge(dodge.width=0.20), size=2) +
        geom_errorbar(aes(group = Type), stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1), position = position_dodge(width=0.20), width = 0.2, size = 1.25, alpha = 0.45) + 
        stat_summary(aes(group = Type), fun = mean, geom = "point", shape = 45, size = 18, position = position_dodge(width=0.20)) + 
        
        scale_color_manual(values = RColorBrewer::brewer.pal(3, "Dark2")[1:2], labels=c("Actual", "Predicted")) + 
        scale_x_continuous(name = "Years", breaks = c(0:100), labels=c(0:100)) + 
        scale_y_continuous(name = "ADAS-Cog 11") + 
        expand_limits(x = c(min(.dat[[group_var]], max(.dat[[group_var]])))) + 
        
        theme_explorer
      
   return(plot_curr)
  
  
}



plot_diff_cdr_rebuild <- function(.dat, allrows){
  group_var <- "time"
  
  plot_curr <- 
        ggplot(data = .dat[!.dat$misclass == "Correct",], aes_string(x = group_var)) + 
        geom_bar(aes(y=(..count..)/(sum(..count..) + (allrows - nrow(.dat))), fill = misclass), position = position_dodge(0.40), width = 0.35, color = "black") + 
        
        scale_fill_brewer(breaks = c("False Positive", "False Negative"), type = "qual", palette = "Set1") + 
        scale_y_continuous(name = "Proportion misclassified", labels = scales::percent_format()) + 
        scale_x_continuous(name = "Years", breaks=c(0:100), labels=c(0:100)) + 
        expand_limits(x = c(min(.dat[[group_var]], max(.dat[[group_var]])))) + 
        
        theme_explorer
  
  return(plot_curr)
}


plot_pred_cdr_rebuild <- function(.dat){
  group_var <- "time"
  outcome <- "CDRSTAT"
  
  plot_curr <- 
      ggplot(data = .dat[.dat[[outcome]]!=0,], aes_string(x = group_var,)) + 
      geom_bar(aes(fill = Type), position = position_dodge(0.40), width = 0.35, color = "black") + 
      
      scale_fill_manual(values = RColorBrewer::brewer.pal(3, "Dark2")[1:2], labels=c("Actual", "Predicted"), drop = FALSE) + 
      scale_y_continuous(name = "N Impaired (CDR 0.5+)") + 
      scale_x_continuous(name = "Years", breaks=c(0:100), labels=c(0:100)) +
      expand_limits(x = c(min(.dat[[group_var]], max(.dat[[group_var]])))) + 
        
      theme_explorer
      
  return(plot_curr)
}






```


## Results - ADAS CPAD

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

dir.base <- "E:/UAB SOPH/Dissertation/Full Project - Meta Database/"

merf.dir <- paste0(dir.base, "MERF/From Cheaha/_targets/objects/")

adas_plot <- readRDS(paste0(merf.dir, "refmod_adas_eval_plots"))

adas_eval <- adas_ref <- readRDS(paste0(merf.dir, "refmod_adas_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cont(rbind(adas_eval[[1]]$Group, adas_eval[[1]]$All))
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=18, full_width =F)

tab_curr

```

]


---

## Results - ADAS CPAD Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(merf.dir, "refmod_adas_eval_plots_obs_noRE"))

adas_eval <- adas_ref_obs <- readRDS(paste0(merf.dir, "refmod_adas_holdout_eval_obs_noRE"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
$~$
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cont(rbind(adas_eval[[1]]$Group, adas_eval[[1]]$All))
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=18, full_width =F)

tab_curr

```

]

---


## Results - Logistic CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(merf.dir, "refmod_cdr_eval_plots"))

cdr_eval <- cdr_ref <- readRDS(paste0(merf.dir, "refmod_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$ 
```{r, echo=F}
tab_curr_base <- table_proc_cat(rbind(cdr_eval[[1]]$Group, cdr_eval[[1]]$All))
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```

]


---


## Results - Logistic CDR Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(merf.dir, "refmod_cdr_eval_plots_obs_noRE"))

cdr_eval <- cdr_ref_obs <- readRDS(paste0(merf.dir, "refmod_cdr_holdout_eval_obs_noRE"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cat(rbind(cdr_eval[[1]]$Group, cdr_eval[[1]]$All))
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```

]



---


class: center, middle

#Aim 1 Results  
#Ensemble Methods
















---


## Results - MERF ADAS Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

merf.dir <- paste0(dir.base, "MERF/From Cheaha/_targets/objects/")

adas_hyper <- readRDS(paste0(merf.dir, "merf_adas_hyper_results"))

boot_curr <- boot_dat[["merf"]]

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
adas_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(adas_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```




---


## Results - MERF ADAS

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(merf.dir, "merf_adas_eval_plots"))

adas_eval <- readRDS(paste0(merf.dir, "merf_adas_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
#tab_curr_base <- table_proc_cont(rbind(adas_eval[[1]]$Group, adas_eval[[1]]$All))
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr
```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas$results[boot_curr$adas$results$time == "All",], adas_eval[[1]]$All, adas_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - MERF ADAS Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(merf.dir, "merf_adas_eval_plots_obs"))

adas_eval <- readRDS(paste0(merf.dir, "merf_adas_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas_obs$results[boot_curr$adas_obs$results$time == "All",], adas_eval[[1]]$All, adas_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]





---


## Results - MERF CDR Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_hyper <- readRDS(paste0(merf.dir, "merf_cdr_hyper_results"))

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
cdr_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(cdr_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```


---


## Results - MERF CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(merf.dir, "merf_cdr_eval_plots"))

cdr_eval <- readRDS(paste0(merf.dir, "merf_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[

```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr$results[boot_curr$cdr$results$time == "All",], cdr_eval[[1]]$All, cdr_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - MERF CDR Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(merf.dir, "merf_cdr_eval_plots_obs"))

cdr_eval <- readRDS(paste0(merf.dir, "merf_cdr_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[

```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr_obs$results[boot_curr$cdr_obs$results$time == "All",], cdr_eval[[1]]$All, cdr_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]
















---



```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

glmer.dir <- paste0(dir.base, "MERF_glmer/GLMER_ref/")

```

## Results - GLMER Tree ADAS

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(glmer.dir, "glmertree_ref_adas_eval_plots"))

adas_eval <- readRDS(paste0(glmer.dir, "glmertree_ref_adas_holdout_eval"))

boot_curr <- boot_dat[["glmertree_ref"]]

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas$results[boot_curr$adas$results$time == "All",], adas_eval[[1]]$All, adas_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - GLMER Tree ADAS Obs

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(glmer.dir, "glmertree_ref_adas_eval_plots_obs"))

adas_eval <- readRDS(paste0(glmer.dir, "glmertree_ref_adas_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas_obs$results[boot_curr$adas_obs$results$time == "All",], adas_eval[[1]]$All, adas_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]





---


## Results - GLMER Tree CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(glmer.dir, "glmertree_ref_cdr_eval_plots"))

cdr_eval <- readRDS(paste0(glmer.dir, "glmertree_ref_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr$results[boot_curr$cdr$results$time == "All",], cdr_eval[[1]]$All, cdr_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - GLMER Tree CDR Obs

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(glmer.dir, "glmertree_ref_cdr_eval_plots_obs"))

cdr_eval <- readRDS(paste0(glmer.dir, "glmertree_ref_cdr_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr_obs$results[boot_curr$cdr_obs$results$time == "All",], cdr_eval[[1]]$All, cdr_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]











---


## Results - Bagged ADAS Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

glmer.dir <- paste0(dir.base, "MERF_glmer/Assembly/")

adas_hyper <- readRDS(paste0(glmer.dir, "glmertree_bagged_adas_hyper_results"))

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
adas_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(adas_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```




---


## Results - Bagged ADAS

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(glmer.dir, "glmertree_bagged_adas_eval_plots"))

adas_eval <- readRDS(paste0(glmer.dir, "glmertree_bagged_adas_holdout_eval"))

boot_curr <- boot_dat[["glmertree_bagged"]]

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas$results[boot_curr$adas$results$time == "All",], adas_eval[[1]]$All, adas_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - Bagged ADAS Obs

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(glmer.dir, "glmertree_bagged_adas_eval_plots_obs"))

adas_eval <- readRDS(paste0(glmer.dir, "glmertree_bagged_adas_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas_obs$results[boot_curr$adas_obs$results$time == "All",], adas_eval[[1]]$All, adas_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]





---


## Results - Bagged CDR Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_hyper <- readRDS(paste0(glmer.dir, "glmertree_bagged_cdr_hyper_results"))

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
cdr_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(cdr_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```


---


## Results - Bagged CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(glmer.dir, "glmertree_bagged_cdr_eval_plots"))

cdr_eval <- readRDS(paste0(glmer.dir, "glmertree_bagged_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr$results[boot_curr$cdr$results$time == "All",], cdr_eval[[1]]$All, cdr_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - Bagged CDR Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(glmer.dir, "glmertree_bagged_cdr_eval_plots_obs"))

cdr_eval <- readRDS(paste0(glmer.dir, "glmertree_bagged_cdr_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr_obs$results[boot_curr$cdr_obs$results$time == "All",], cdr_eval[[1]]$All, cdr_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]










---


## Results - Boosted ADAS Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

glmer.dir <- paste0(dir.base, "MERF_mvt/From Cheaha/_targets/objects/")

adas_hyper <- readRDS(paste0(glmer.dir, "mvtboost_adas_hyper_results"))

boot_curr <- boot_dat[["mvtboost"]]

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
adas_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(adas_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```




---


## Results - Boosted ADAS

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(glmer.dir, "mvtboost_adas_eval_plots"))

adas_eval <- readRDS(paste0(glmer.dir, "mvtboost_adas_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas$results[boot_curr$adas$results$time == "All",], adas_eval[[1]]$All, adas_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - Boosted ADAS Obs

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(glmer.dir, "mvtboost_adas_eval_plots_obs"))

adas_eval <- readRDS(paste0(glmer.dir, "mvtboost_adas_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=18, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas_obs$results[boot_curr$adas_obs$results$time == "All",], adas_eval[[1]]$All, adas_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]





---


## Results - Boosted CDR Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_hyper <- readRDS(paste0(glmer.dir, "mvtboost_cdr_hyper_results"))

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
cdr_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(cdr_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```


---


## Results - Boosted CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(glmer.dir, "mvtboost_cdr_eval_plots"))

cdr_eval <- readRDS(paste0(glmer.dir, "mvtboost_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr$results[boot_curr$cdr$results$time == "All",], cdr_eval[[1]]$All, cdr_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - Boosted CDR Obs

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(glmer.dir, "mvtboost_cdr_eval_plots_obs"))

cdr_eval <- readRDS(paste0(glmer.dir, "mvtboost_cdr_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr_obs$results[boot_curr$cdr_obs$results$time == "All",], cdr_eval[[1]]$All, cdr_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]

---



















class: center, middle

#Aim 2 Results  
#Neural Network Methods





---


## Results - FNN ADAS Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

nn.dir <- paste0(dir.base, "Neural Nets/_targets/objects/")

adas_hyper <- readRDS(paste0(nn.dir, "fnn_adas_hyper_results"))

boot_curr <- boot_dat[["fnn"]]

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
adas_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(adas_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```




---


## Results - FNN ADAS

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(nn.dir, "fnn_adas_eval_plots"))

adas_eval <- readRDS(paste0(nn.dir, "fnn_adas_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas$results[boot_curr$adas$results$time == "All",], adas_eval[[1]]$All, adas_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - FNN ADAS Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(nn.dir, "fnn_adas_eval_plots_obs"))

adas_eval <- readRDS(paste0(nn.dir, "fnn_adas_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas_obs$results[boot_curr$adas_obs$results$time == "All",], adas_eval[[1]]$All, adas_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]





---


## Results - FNN CDR Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_hyper <- readRDS(paste0(nn.dir, "fnn_cdr_hyper_results"))

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
cdr_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(cdr_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```


---


## Results - FNN CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(nn.dir, "fnn_cdr_eval_plots"))

cdr_eval <- readRDS(paste0(nn.dir, "fnn_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr$results[boot_curr$cdr$results$time == "All",], cdr_eval[[1]]$All, cdr_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - FNN CDR Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(nn.dir, "fnn_cdr_eval_plots_obs"))

cdr_eval <- readRDS(paste0(nn.dir, "fnn_cdr_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr_obs$results[boot_curr$cdr_obs$results$time == "All",], cdr_eval[[1]]$All, cdr_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]














---


## Results - CNN ADAS Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

nn.dir <- paste0(dir.base, "Neural Nets/_targets/objects/")

adas_hyper <- readRDS(paste0(nn.dir, "cnn_adas_hyper_results"))

boot_curr <- boot_dat[["cnn"]]

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
adas_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(adas_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```




---


## Results - CNN ADAS

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(nn.dir, "cnn_adas_eval_plots"))

adas_eval <- readRDS(paste0(nn.dir, "cnn_adas_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas$results[boot_curr$adas$results$time == "All",], adas_eval[[1]]$All, adas_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - CNN ADAS Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(nn.dir, "cnn_adas_eval_plots_obs"))

adas_eval <- readRDS(paste0(nn.dir, "cnn_adas_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas_obs$results[boot_curr$adas_obs$results$time == "All",], adas_eval[[1]]$All, adas_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]





---


## Results - CNN CDR Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_hyper <- readRDS(paste0(nn.dir, "cnn_cdr_hyper_results"))

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
cdr_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(cdr_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```


---


## Results - CNN CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(nn.dir, "cnn_cdr_eval_plots"))

cdr_eval <- readRDS(paste0(nn.dir, "cnn_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr$results[boot_curr$cdr$results$time == "All",], cdr_eval[[1]]$All, cdr_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - CNN CDR Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(nn.dir, "cnn_cdr_eval_plots_obs"))

cdr_eval <- readRDS(paste0(nn.dir, "cnn_cdr_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr_obs$results[boot_curr$cdr_obs$results$time == "All",], cdr_eval[[1]]$All, cdr_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]















---


## Results - LSTM ADAS Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

nn.dir <- paste0(dir.base, "Neural Nets/_targets/objects/")

adas_hyper <- readRDS(paste0(nn.dir, "lstm_adas_hyper_results"))

boot_curr <- boot_dat[["lstm"]]

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
adas_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(adas_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```




---


## Results - LSTM ADAS

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(nn.dir, "lstm_adas_eval_plots"))

adas_eval <- readRDS(paste0(nn.dir, "lstm_adas_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas$results[boot_curr$adas$results$time == "All",], adas_eval[[1]]$All, adas_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - LSTM ADAS Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

adas_plot <- readRDS(paste0(nn.dir, "lstm_adas_eval_plots_obs"))

adas_eval <- readRDS(paste0(nn.dir, "lstm_adas_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_adas_rebuild(adas_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_adas_rebuild(adas_plot[[1]]$diff$data)

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cont(adas_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```
$~$
```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$adas_obs$results[boot_curr$adas_obs$results$time == "All",], adas_eval[[1]]$All, adas_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               #caption = "Across all times"
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]





---


## Results - LSTM CDR Hyper

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_hyper <- readRDS(paste0(nn.dir, "lstm_cdr_hyper_results"))

```


```{r, echo=F, fig.width=7, fig.height=4.5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}
cdr_hyper$plot
```
$~$
```{r, echo=F}
tab_curr_base <- tab_proc_hyper(cdr_hyper$best[,-1])
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("cccc"),
               escape=F, linesep="")
tab_curr <- kable_styling(tab_curr, font_size=16, full_width =F)

tab_curr

```


---


## Results - LSTM CDR

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(nn.dir, "lstm_cdr_eval_plots"))

cdr_eval <- readRDS(paste0(nn.dir, "lstm_cdr_holdout_eval"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr$results[boot_curr$cdr$results$time == "All",], cdr_eval[[1]]$All, cdr_ref[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]


---


## Results - LSTM CDR Observations

```{r, echo=F, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

cdr_plot <- readRDS(paste0(nn.dir, "lstm_cdr_eval_plots_obs"))

cdr_eval <- readRDS(paste0(nn.dir, "lstm_cdr_holdout_eval_obs"))

```

.pull-left[

```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_pred_cdr_rebuild(cdr_plot[[1]]$plot$data)

```


```{r, echo=F, fig.width=7.5, fig.height=5, out.extra='style="margin-left: auto; margin-right:auto; display: block"'}

plot_diff_cdr_rebuild(cdr_plot[[1]]$diff$data, nrow(cdr_plot[[1]]$plot$data))

```

]

.pull-right[
$~$
```{r, echo=F}
tab_curr_base <- table_proc_cat(cdr_eval[[1]]$Group)
tab_curr <- 
  knitr::kable(tab_curr_base, "html",
               align = c("ccc"),
               escape=F, linesep="")
#tab_curr <- row_spec(tab_curr, nrow(tab_curr_base), bold=T)
tab_curr <- kable_styling(tab_curr, font_size=14, full_width =F)

tab_curr

```

```{r, echo=F}
tab_boot_base <- tab_proc_boot(boot_curr$cdr_obs$results[boot_curr$cdr_obs$results$time == "All",], cdr_eval[[1]]$All, cdr_ref_obs[[1]]$All)
tab_boot <- 
  knitr::kable(tab_boot_base[["tab"]], "html",
               align = rep("c",6),
               escape=F, linesep="",
               caption = tab_boot_base[["NRI"]]
               )
tab_boot <- kable_styling(tab_boot, font_size=14, full_width =F)

tab_boot

```

]

---

#Results - ADAS Compare

```{r, echo = F, tidy=FALSE}

comp_curr_base <- comp_table[[1]]$RMSE
caption_curr <- "RMSE"

comp_curr <- 
  knitr::kable(comp_curr_base, "html", 
               align = rep("c", ncol(comp_curr_base)),
               escape = FALSE, linesep = "",
               caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
comp_curr <- column_spec(comp_curr, 1, bold=T)
comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)

comp_curr

```



---

#Results - ADAS Compare

```{r, echo = F, tidy=FALSE}

comp_curr_base <- comp_table[[1]][["Median AE"]]
caption_curr <- "Median AE"

comp_curr <- 
  knitr::kable(comp_curr_base, "html", 
               align = rep("c", ncol(comp_curr_base)),
               escape = FALSE, linesep = "",
               caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
comp_curr <- column_spec(comp_curr, 1, bold=T)
comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)

comp_curr

```



---

#Results - ADAS Compare

```{r, echo = F, tidy=FALSE}

comp_curr_base <- comp_table[[1]]$Bias
caption_curr <- "AV Bias"

comp_curr <- 
  knitr::kable(comp_curr_base, "html", 
               align = rep("c", ncol(comp_curr_base)),
               escape = FALSE, linesep = "",
               caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
comp_curr <- column_spec(comp_curr, 1, bold=T)
comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)

comp_curr

```




---

#Results - CDR Compare

```{r, echo = F, tidy=FALSE}

comp_curr_base <- comp_table[[2]]$Accuracy
caption_curr <- "Accuracy"

comp_curr <- 
  knitr::kable(comp_curr_base, "html", 
               align = rep("c", ncol(comp_curr_base)),
               escape = FALSE, linesep = "",
               caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
comp_curr <- column_spec(comp_curr, 1, bold=T)
comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)

comp_curr

```


---

#Results - CDR Compare

```{r, echo = F, tidy=FALSE}

comp_curr_base <- comp_table[[2]]$Precision
caption_curr <- "Precision"

comp_curr <- 
  knitr::kable(comp_curr_base, "html", 
               align = rep("c", ncol(comp_curr_base)),
               escape = FALSE, linesep = "",
               caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
comp_curr <- column_spec(comp_curr, 1, bold=T)
comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)

comp_curr

```
---

#Results - CDR Compare

```{r, echo = F, tidy=FALSE}

comp_curr_base <- comp_table[[2]]$Recall
caption_curr <- "Recall"

comp_curr <- 
  knitr::kable(comp_curr_base, "html", 
               align = rep("c", ncol(comp_curr_base)),
               escape = FALSE, linesep = "",
               caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
comp_curr <- column_spec(comp_curr, 1, bold=T)
comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)

comp_curr

```
---

#Results - CDR Compare

```{r, echo = F, tidy=FALSE}

comp_curr_base <- comp_table[[2]]$AUC
caption_curr <- "AUC"

comp_curr <- 
  knitr::kable(comp_curr_base, "html", 
               align = rep("c", ncol(comp_curr_base)),
               escape = FALSE, linesep = "",
               caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
comp_curr <- column_spec(comp_curr, 1, bold=T)
comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)

comp_curr

```





---





class: center, middle

#Aim 3 Results  
#Random Effects Imputation and
#Impact on ADAS-Cog Prediction




---




```{r, include = F}

eval_true <- readRDS(paste0(dir.base, "RandEff Impute/impute_true.rds"))
xx <- eval_true$merf_obs_fit_eval$All$Bias; xx2 <- eval_true$merf_obs_fit_eval$Group$Bias
yy <- eval_true$merf_obs_impute_eval$All$Bias; yy2 <- eval_true$merf_impute_fit_eval$Group$Bias
eval_true$merf_obs_impute_eval$All$Bias <- eval_true$merf_obs_noRE_eval$All$Bias
eval_true$merf_obs_impute_eval$Group$Bias <- eval_true$merf_obs_noRE_eval$Group$Bias
eval_true$merf_obs_noRE_eval$All$Bias <- xx; eval_true$merf_obs_noRE_eval$Group$Bias <- xx2
eval_true$merf_obs_fit_eval$All$Bias <- yy; eval_true$merf_obs_fit_eval$Group$Bias <- yy2

eval_synth <- readRDS(paste0(dir.base, "RandEff Impute/impute_synth.rds"))


impute_table_base <- impute_table_builder(eval_true)

impute_table <- 
  knitr::kable(impute_table_base, "html", 
               align = rep("c", ncol(impute_table_base)),
               escape = FALSE, linesep = "",
               #caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
impute_table <- row_spec(impute_table, c(1:nrow(impute_table_base)), extra_css = "vertical-align: middle !important;")
impute_table <- kable_styling(impute_table, font_size=14, full_width = FALSE)

impute_table

```











