---
title: "Applications of Longitudinal Machine Learning Methods in Multi-Study Alzheimer’s Disease Datasets"
subtitle: "PhD Dissertation Defense for<br>Doctorate Degree in Biostatistics"
author: "Charles Murchison"
institute: "Department of Biostatistics<br>Alzheimer's Disease Research Center"
date: "11/10/2021"
output:
  xaringan::moon_reader:
    css: [default, robot, robot-fonts, extra.css]
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    lib_dir: libs
    nature:
      titleSlideClass: ["center", "middle"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}

R.utils::sourceDirectory("./R/", modifiedOnly = FALSE)

suppressPackageStartupMessages({
  library(shiny)
  library(knitr)
  library(kableExtra)
  library(ggplot2)
})

options(knitr.kable.NA = '')
opts_chunk$set(tidy = FALSE)

boot_dat <- readRDS("boot_data.rds")
comp_table <- readRDS("boot_compare_wobs.rds")  #Use boot_compare.rds if you don't want to combine observations


eval_true <- readRDS(paste0(dir.base, "RandEff Impute/impute_true.rds"))
eval_synth <- readRDS(paste0(dir.base, "RandEff Impute/impute_synth.rds"))



data_curr_orig <- readRDS(paste0(dir.base, "MERF/_targets/objects/holdout_split_dat"))
dat <- data_curr_orig$all
dat_bl <- data_curr_orig$bl

dat_retain <- dat_bl$retained
dat_holdout <- dat_bl$holdout

dat_holdout <- data_curr_orig$all$holdout[data_curr_orig$all$holdout$VISTIME==0,]
dat_retain <- data_curr_orig$all$retain[data_curr_orig$all$retain$VISTIME==0,]

obs_id <- unique(dat$holdout_obs$UID)
dat_obs <- dat_retain[dat_retain$UID %in% obs_id,]
dat_obs2 <- dat$holdout_obs

covarset <- tab1_dict[["var_names"]]
covarset <- covarset[-which(covarset == "ADASTOTAL11")]

for(ii in 1:length(covarset)){
  dat_retain <- dat_retain[!is.na(dat_retain[[covarset[ii]]]),]
  dat_holdout <- dat_holdout[!is.na(dat_holdout[[covarset[ii]]]),]
  dat_obs <- dat_obs[!is.na(dat_obs[[covarset[ii]]]),]
  dat_obs2 <- dat_obs2[!is.na(dat_obs2[[covarset[ii]]]),]
  
}

#dat_retain <- dat_retain[-which(is.na(dat_retain$CDRSTAT) & is.na(dat_retain$ADASTOTAL11)),]
#dat_holdout <- dat_holdout[-which(is.na(dat_holdout$CDRSTAT) & is.na(dat_holdout$ADASTOTAL11)),]
#dat_obs <- dat_obs[-which(is.na(dat_obs$CDRSTAT) & is.na(dat_obs$ADASTOTAL11)),]

tab1_retain <- table1_build(dat_retain)
tab1_holdout <- table1_build(dat_holdout)
tab1_obs <- table1_build(dat_obs)




tab1_base <- do.call(cbind, list(tab1_retain, tab1_holdout[,-1], tab1_obs[,-1]))
cat_vars <- grep("\\(", tab1_base[,2])
tab1_cont_base <- tab1_base[-cat_vars,]
tab1_cat_base <- tab1_base[cat_vars,]
rownames(tab1_cont_base) <- rownames(tab1_cat_base) <- NULL

tab1_cont <- 
  knitr::kable(tab1_cont_base, "html", 
               align = c("l", rep("c", ncol(tab1_cont_base)-1)),
               escape = FALSE, linesep = "",
               #caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
tab1_cont <- row_spec(tab1_cont, c(1:nrow(tab1_cont_base)), extra_css = "vertical-align: middle !important;")

tab1_cont <- add_header_above(tab1_cont, c( " ", "Training Dataset" = 3, "Trajectory Holdouts" = 3, "Observation Holdouts" = 3))
#tab1_cont <- pack_rows(tab1_cont, "Whole\n Trajectories", 1, 2, label_row_css = "background_color")
#tab1_cont <- pack_rows(tab1_cont, "Observation\n Forecasts", 3, 5)

tab1_cont <- column_spec(tab1_cont, c(1,4,7), border_right = T)
tab1_cont <- column_spec(tab1_cont, c(1), width="7em", bold=T)


tab1_cont <- kable_styling(tab1_cont, font_size=12, full_width = FALSE)
tab1_cont <- row_spec(tab1_cont, c(1), extra_css = "border-top: 1px solid")




tab1_cat <- 
  knitr::kable(tab1_cat_base, "html", 
               align = c("l", rep("c", ncol(tab1_cat_base)-1)),
               escape = FALSE, linesep = "",
               #caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
               )
tab1_cat <- row_spec(tab1_cat, c(1:nrow(tab1_cat_base)), extra_css = "vertical-align: middle !important;")

tab1_cat <- add_header_above(tab1_cat, c( " ", "Training Dataset" = 3, "Trajectory Holdouts" = 3, "Observation Holdouts" = 3))
#tab1_cat <- pack_rows(tab1_cat, "Whole\n Trajectories", 1, 2, label_row_css = "background_color")
#tab1_cat <- pack_rows(tab1_cat, "Observation\n Forecasts", 3, 5)

tab1_cat <- column_spec(tab1_cat, c(1,4,7), border_right = T)
tab1_cat <- column_spec(tab1_cat, c(1), width="7em", bold=T)
tab1_cat <- row_spec(tab1_cat, c(1,2,4,6,7,12), extra_css = "border-top: 1px solid")


tab1_cat <- kable_styling(tab1_cat, font_size=12, full_width = FALSE)






```

##Approach - Final Dataset


```{r, echo=F}
tab1_cont
```

<div style = "font-size: 18px; text-align: left;"><br>Continuous variables presented as mean ± standard deviaion<br>
<br>Categorical variables on the following slide presented as counts with<br>proportions in parenthesis based on column margins</div>

---

##Approach - Final Dataset


```{r, echo=F}
tab1_cat
```

---

## Synth Results - RE Design Comparison

```{r, echo = F}


# 
# comp_impute_base <- impute_compare_builder(eval_synth, obs = FALSE)
# 
# 
# comp_impute <- 
#   knitr::kable(comp_impute_base, "html", 
#                align = rep("c", ncol(comp_impute_base)),
#                escape = FALSE, linesep = "",
#                #caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
#                )
# comp_impute <- row_spec(comp_impute, c(1:nrow(comp_impute_base)), extra_css = "vertical-align: middle !important;")
# #comp_impute <- row_spec(comp_impute, 1, extra_css = "border-top: 1px solid;")
# comp_impute <- column_spec(comp_impute, 1, bold=T, width = "50em") #, border_right = TRUE)
# comp_impute <- column_spec(comp_impute, c(2:(nrow(comp_impute_base)+1)), width = "30em")
# comp_impute <- kable_styling(comp_impute, font_size=14, full_width = FALSE)
# 
# comp_impute


```



---

## Synth Results - RE Compare Obs

```{r, echo = F}


# 
# comp_impute_base <- impute_compare_builder(eval_synth, obs = TRUE)
# 
# 
# comp_impute <- 
#   knitr::kable(comp_impute_base, "html", 
#                align = rep("c", ncol(comp_impute_base)),
#                escape = FALSE, linesep = "",
#                #caption = paste0("<div style=\"color:black; font-size:24px\">", caption_curr, "</div>")
#                )
# comp_impute <- row_spec(comp_impute, c(1:nrow(comp_impute_base)), extra_css = "vertical-align: middle !important;")
# #comp_impute <- row_spec(comp_impute, 1, extra_css = "border-top: 1px solid;")
# comp_impute <- column_spec(comp_impute, 1, bold=T, width = "50em") #, border_right = TRUE)
# comp_impute <- column_spec(comp_impute, c(2:(nrow(comp_impute_base)+1)), width = "30em")
# comp_impute <- kable_styling(comp_impute, font_size=14, full_width = FALSE)
# 
# comp_impute

```


---



---
---

<h2 style="font-size: 40px; margin-bottom: 5px">ML/SL Comparison - ADAS Regression</h2>

```{r, echo = F, tidy=FALSE}

# comp_curr_base <- comp_table[[1]]$RMSE
# caption_curr <- "RMSE"
# 
# comp_curr <- 
#   knitr::kable(comp_curr_base, "html", 
#                align = rep("c", ncol(comp_curr_base)),
#                escape = FALSE, linesep = "",
#                caption = paste0("<div style=\"color:black; font-size:32px\">", caption_curr, "</div>")
#                )
# comp_curr <- row_spec(comp_curr, c(1:nrow(comp_curr_base)), extra_css = "vertical-align: middle !important;")
# comp_curr <- column_spec(comp_curr, 1, bold=T)
# comp_curr <- kable_styling(comp_curr, font_size=14, full_width = FALSE)
# 
# comp_curr

```
<div style = "font-size: 18px; text-align: center;">Trajectory comparisons in lower half of matrix with forecast comparisons in upper half<br>
Direction of comparisons is column model relative to row model</div>


---



